MSCI 718 Mini-Project: COVID-19 Time Series Analysis and Visualization

### 2020-04-23 MSCI718 2020W Project v3.Rmd
Added more description to Data section and references

Firstly, a Global COVID-19 Report dataset was sourced from Kaggle with 15,170 observations. This dataset included daily entries of cumulative number of cases of COVID-19 for 185 countries, each with 82 entries dating from January 22nd, 2020 to April 12th, 2020. The following were the relevant variables from the dataset that were used for the analysis:

@@

```{r, echo = FALSE,message=FALSE, error = FALSE,fig.height=2.8}
a <- ggplot(confirmed_df,aes(Confirmed)) + geom_histogram() + stat_bin(aes(y=..count.., label =..count..),geom="text",size=2,vjust=-0.3) + ggtitle("Frequency of Confirmed Cases") + ylab("Frequency")
a
```
&nbsp;

@@

A country that has done really well in containing the virus is South Korea. As demonstrated by the linear growth, South Korea started with an exponential growth like every other country, but their effective social distancing and rapid testing measures is reflected in the graph's sharp dip.

@@

>>>>

Firstly, a Global COVID-19 Report dataset was sourced from Kaggle with 15,170 observations. This dataset included daily entries of cumulative number of cases of COVID-19 for 185 countries, each with 82 entries dating from January 22nd, 2020 to April 12th, 2020. However, the first case of COVID-19 was recorded in November 2019 [Bryner]. In addition, the actual number of cases in a country may differ from the reported number. For this analysis, we assumed that this data was accurate. The following were the relevant variables from the dataset that were used for the analysis:

@@

```{r, echo = FALSE,message=FALSE, error = FALSE,fig.height=2.5}
a <- ggplot(confirmed_df,aes(Confirmed)) + geom_histogram() + stat_bin(aes(y=..count.., label =..count..),geom="text",size=2,vjust=-0.3) + ggtitle("Frequency of Confirmed Cases") + ylab("Frequency")
a
```
&nbsp;

@@

A country that has done really well in containing the virus is South Korea [Bhatia]. As demonstrated by the linear growth, South Korea started with an exponential growth like every other country, but their effective social distancing and rapid testing measures is reflected in the graph's sharp dip.

@@

Bhatia, Aatish. “Covid Trends.” aatishb.com/covidtrends/.

Bryner, Jeanna. “1st Known Case of Coronavirus Traced Back to November in China.” LiveScience, Purch, 14 Mar. 2020, www.livescience.com/first-case-coronavirus-found.html.
